Mental Health Screening in CF

### 2023-01-05 Emily Muther/mental_health_screening.qmd
Update mental_health_screening.qmd

---
title: "Mental Health Screening in CF"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: visual
---

```{r}
#| include: false
library(tidyverse)
library(lubridate)
```

```{r}
# Data import
cf_gad = read.csv("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/GAD-7_General_Anxiety_Disorder_Full_Data_data_11-15-22.csv",na.strings = "")
cf_phq = read.csv("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PHQ-9_Full_Data_data_11-11-22.csv",na.strings = "")
cf_psc = read.csv("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv",na.strings = "")
# Select and merge
cf_gad = cf_gad %>% select(PAT_MRN_ID,CONTACT_DATE,GAD.7.Total.Score,GAD.7.Totals) %>% drop_na()
cf_phq = cf_phq %>% 
  select(PAT_MRN_ID,CONTACT_DATE,PHQ.9.Total.Score..calculated.,PHQ.9.Totals) %>% drop_na()
cf_psc = cf_psc %>% select(PAT_MRN_ID,CONTACT_DATE,Score,PSC.Totals) %>% drop_na()
df = cf_gad %>% 
  full_join(cf_phq,by = c("PAT_MRN_ID", "CONTACT_DATE")) %>%
  full_join(cf_psc,by = c("PAT_MRN_ID", "CONTACT_DATE"))
# Get age
pa = read.csv("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/CF_Psychosocial_Assessment_Full_Data_data_11-15-22.csv",na.strings = "")
pa = pa %>% select(PAT_MRN_ID,CONTACT_DATE,AGE_AT_CONTACT_IN_YEARS)
# Rename columns, get distinct rows
df = left_join(df,pa,by = c("PAT_MRN_ID", "CONTACT_DATE")) %>% 
  select(PAT_MRN_ID,CONTACT_DATE,AGE_AT_CONTACT_IN_YEARS,everything()) %>%
  rename(id = PAT_MRN_ID,date = CONTACT_DATE,age=AGE_AT_CONTACT_IN_YEARS,
         `GAD-7 Total` = GAD.7.Total.Score,
         `GAD-7 Category`=GAD.7.Totals,
         `PHQ-9 Total`=PHQ.9.Total.Score..calculated.,
         `PHQ-9 Category`=PHQ.9.Totals,
         `PSC-17 Total`=Score,
         `PSC-17 Category`=PSC.Totals) %>%
  distinct()
df$date = parse_date(df$date,approx = F)
df = df %>% arrange(id,date)
```

# Table

```{r}
#| label: tbl-planets
#| tbl-cap: Planets

```

# Figure

```{r}
#| label: fig-planets
#| fig-cap: Planets

```

>>>>

---
title: "Mental Health Screening in CF"
author: "Tim Vigers"
date: last-modified
format:
  html:
    code-fold: true
    self-contained: true
    page-layout: full
    title-block-banner: true
editor: source
---

# Data Cleaning

```{python}
import pandas as pd
# Data import
gad7 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/GAD-7_General_Anxiety_Disorder_Full_Data_data_11-15-22.csv")
gad7 = gad7[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','GAD-7 Total Score','GAD-7 Totals']]
gad7.dropna(axis=0,inplace=True)
gad7.drop_duplicates(inplace=True)
phq9 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PHQ-9_Full_Data_data_11-11-22.csv")
phq9 = phq9[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','PHQ-9 Total Score (calculated)','PHQ-9 Totals']]
phq9.dropna(axis=0,inplace=True)
phq9.drop_duplicates(inplace=True)
psc = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv")
psc = psc[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','Score','PSC Totals']]
psc.dropna(axis=0,inplace=True)
psc.drop_duplicates(inplace=True)
# Merge
df = gad7.merge(phq9,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
df = df.merge(psc,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
# Rename
df.rename({'PAT_MRN_ID':'ID','CONTACT_DATE':'Date','AGE AT CONTACT ':'Age','GAD-7 Total Score':'GAD-7 Total','GAD-7 Totals':'GAD-7 Group','PHQ-9 Total Score (calculated)':'PHQ-9 Total','PHQ-9 Totals':'PHQ-9 Group','Score':'PSC-17 Total','PSC Totals':'PSC-17 Group'},inplace=True,axis=1)
```

- On first import, there are 2,646 observations each for GAD-7, PHQ-9, and PSC-17. 
- After deleting rows missing any any of patient ID, contact date, age at contact, total score, or score group, there were: 
  - 559 observations for GAD-7
  - 548 for PHQ-9
  - 308 for PSC-17
- After dropping duplicate rows, there are: 
  - 390 GAD-7 observations
  - 383 for PHQ-9
  - 216 for PSC-17
- After merging these together based on ID, date, and age, there are 613 unique observations with at least one of the three screening measures.

# Profiling

```{python}
from pandas_profiling import ProfileReport
profile = ProfileReport(df, title="Data Profiling Report")
profile.to_notebook_iframe()
```
